::: {.callout-warning}
## On the simplified nature of analysis in this document. 

Subject of financial analysis is very information-dense and to perform such an analysis (be it an analysis of industrial sectors, fundamental, technical, etc.) in earnest is a non-trivial job that we don't see ourselves capable of performing.

Therefore, this document aims to provide a simplified, non-rigorous analysis aiming to showcase our understanding of course material and minimal proficiency in scientific communication using tools such as DeepSeek LLM with Web Search functionality, R language [@ProjectStatisticalComputing], its "tidyquant" package [@danchoTidyquantTidyQuantitative2025] and Quarto scientific publishing system [@Quarto].
:::

```{r} 
plot(rnorm(100))
```

We need better stuff though.

```{r} 
#| label: tbl-planets
#| tbl-cap: Astronomical object
library(quantmod)
getSymbols('CPALTT01USQ657N',src = 'FRED')
cpi.changes <- CPALTT01USQ657N
head(cpi.changes)
summary(cpi.changes)
plot(cpi.changes,main='CPI',ylab='%',xlab='Time')
```

Use this kind of macroeconomic analysis maybe?
