<!--
Common size analysis for fundamental analysis.
Life cycle stage.
ROI for stock over a period of time.
Analyst's views and rating.
client.shwab.com
EBITDA
P/B ratio
EV = Mcap + Debt
-->

::: {.callout-note}
In this section we will take a look at quantitative fundamental analysis tools provided by the "tidyquant" R language package [@danchoTidyquantTidyQuantitative2025] and use them to get key financial ratios of fundamental analysis for the Clorox company. This section is based on the following wonderful tutorial: @PerformanceAnalysisTidyquant
:::

#### **Basic Fundamental Analysis of the Clorox Company**

First let's retrieve 5-year period returns from the prices adjusted for stock splits, both for Clorox and S&P500 as the baseline. Next, we combine both datasets (Clorox and S&P500 returns) using "left-join" on the "date" field. Using this dataset, we can retrieve all kind of fundamental metrics, such as **Alpha** (0.0008), **Beta** (0.414).

```{r}
#| echo: true
library(tidyverse)
library(tidyquant)

Ra <- "CLX" |>
    tq_get(get  = "stock.prices",
           from = "2020-01-01",
           to   = "2025-02-01") |>
    group_by(symbol) |>
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Ra")


Rb <- "^GSPC" |>
    tq_get(get  = "stock.prices",
           from = "2020-01-01",
           to   = "2025-02-01") |>
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Rb")

RaRb <- left_join(Ra, Rb, by = c("date" = "date"))


RaRb_capm <- RaRb %>%
    tq_performance(Ra = Ra, 
                   Rb = Rb, 
                   performance_fun = table.CAPM)

RaRb_capm %>% select(symbol, Alpha, Beta) |> print()


```

We can also get the **Annualized Sharpe Ratio and Returns**, **Types of Mean Return (Geometric, Arithmetic, etc.)**, **Kurtosis**, as well as **Maximum and Median Return** by following the similar steps (no need for the baseline this time).

```{r} 
#| echo: true
library(tidyverse)
library(tidyquant)

Ra <- "CLX" |>
    tq_get(get  = "stock.prices",
           from = "2020-01-01",
           to   = "2025-02-01") |>
    group_by(symbol) |>
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Ra")

Ra |>
  tq_performance(Ra = Ra, Rb = NULL, performance_fun = table.AnnualizedReturns) |>
  print()

Ra |>
  tq_performance(Ra = Ra, Rb = NULL, performance_fun = table.Stats) |>
  print()
```

#### **Conclusion**  
We can use the "tidyquant" R language package to perform fundamental analysis of the company and obtain all of the key financial ratios for such analysis. The analysis shows a company in recovery with strong fundamentals.
