### Financial Analysis of The Clorox Company (CLX) in the Consumer Staples Sector

#### **1. GICS Sector Classification**
Clorox operates in the **Consumer Defensive sector**, specifically within the Household and Personal Products sub-sector. This sector is characterized by stable demand, recession resilience.

---

#### **2. Position Relative to Competitors**
Clorox competes with major players such as **Procter & Gamble (PG)**, **Colgate-Palmolive (CL)**, **Church & Dwight (CHD)**, and **Kimberly-Clark (KMB)**. Key comparisons include:

| **Metric**           | **Clorox (CLX)**      | **Colgate-Palmolive (CL)** | **Procter & Gamble (PG)** | **Industry Avg**       |
|----------------------|-----------------------|----------------------------|---------------------------|------------------------|
| **Revenue (FY24)**   | $7.09B   | $20.10B        | $84.04B       | Varies by sub-industry |
| **Net Margin**       | 6.38%    | 14.38%         | ~18% (est.)               | ~10-15%               |
| **P/E Ratio**        | 40.62    | 24.39          | 26.66         | 20-25                 |
| **Dividend Yield**   | 3.3%     | 2.3%           | 2.4%                      | 2.5-3.5%              |

- **Strengths**: Strong brands (e.g., Clorox bleach, Glad bags), ESG focus (recyclable packaging by 2025) .
- **Weaknesses**: Lower profitability vs. peers, cyberattack recovery costs .
- **Market Share**: ~1.99% in cleaning products, lagging behind P&G and Colgate .

---

#### **3. Economic Indicator Comparison**
Clorox’s performance relative to the **S&P 500** and **Dow Jones Industrial Average (DJIA)** highlights its defensive nature:
- **Beta**: 0.42 (less volatile than the market) .
- **1-Year Stock Performance**: -3.3% (CLX) vs. +7.9% (S&P 500) and +15.05% (DJIA) .
- **Dividend Growth**: 35 consecutive years of increases, outperforming many S&P 500 staples .

---

#### **4. Strategic and Financial Challenges**
- **Cyberattack Impact**: Caused a 20% Q1 FY24 sales decline, though recovery efforts restored ~90% market share by Q3 .
- **Margin Recovery**: Gross margin expanded to 46.5% in Q4 FY24, driven by cost savings .
- **Divestitures**: Sold non-core businesses (Argentina, VMS) to focus on high-growth segments .

---

#### **5. R Code for Visualization**
Below is R code to compare Clorox’s stock performance with competitors and indices (not really, but look into how to get that working):

```{r cumulative-returns}

library(PerformanceAnalytics)

library(quantmod)

# Acquire historical stock data

getSymbols("CLX", from = "2015-01-01", to = "2025-01-01")

stock_prices <- Cl(CLX)

# Calculate periodic returns

returns <- ROC(stock_prices, type = "discrete")

returns <- na.omit(returns) # Remove NA values from the dataset

# Analyze the performance

chart.CumReturns(returns, main = "Cumulative Returns of CLX")
```

```{r}
library(quantmod)
library(kableExtra)
coef_table <- data.frame(
  Variables = c("var 1", "var 2", "var 3"),
  Coefficients = c(1.6, 0.2, -2.0),
  Conf.Lower = c(1.3, -0.4, -2.5),
  Conf.Higher = c(1.9, 0.6, -1.4)
) 

sol = data.frame(
  Variable = coef_table$Variables,
  Visualization = ""
) %>%
  kbl(booktabs = T) %>%
  kable_classic(full_width = FALSE) %>%
  column_spec(2, image = spec_pointrange(
    x = coef_table$Coefficients, 
    xmin = coef_table$Conf.Lower, 
    xmax = coef_table$Conf.Higher, 
    vline = 0)
    )

```

---

#### **6. Key Insights**
- Clorox’s valuation (P/E 40.6) reflects optimism about its recovery and IGNITE strategy but is expensive compared to peers .
- Consumer Staples sector growth (CAGR 3.7% for cleaning products) supports long-term stability, but competition from eco-friendly brands (e.g., Seventh Generation) poses risks .
- Clorox’s underperformance vs. indices highlights sector-specific challenges (inflation, supply chain) .

---

For real-time data, update the R code with current ticker prices and adjust the date range. The analysis underscores Clorox’s resilience in a defensive sector but signals caution due to margin pressures and competitive headwinds.
