<!--
See "technical overview example" in notes. 
Use The Relative Strength Index (RSI).
Overbought/oversold analysis. 
Beta value for 5 years. Open, close, range, average volume, put/call ratios.
Return for ETF vs return for stock over time.
Stock correlation calculator?
Maybe just copy from here: https://mlozanoqf.github.io/tutorial_pmf/#technical-analysis.
-->

::: {.callout-note}
Technical analysis in this section follows the wonderful tutorial provided here: [@FinancialModelingb]
:::

### **Basic Technical Analysis of the Clorox Company**

We'll start with providing a simple plot of stock price movement.

```{r} 
#| echo: true
library(tidyquant)
library(ggplot2)
library(dplyr)
CLX <- tq_get("CLX", get = "stock.prices", from = "2024-01-01", 
               to = "2025-02-01")

CLX |>
    ggplot(aes(x = date, y = close)) + geom_line() +
    labs(y = "Closing price", x = "", title = "Simple plot representing closing prices of the CLX stock for the past year") +
    theme_tq()
```

To identify basic trend in this movement, we then chart the **Simple Moving Average**.

```{r} 
#| echo: true
library(tidyquant)
library(ggplot2)
library(dplyr)
CLX <- tq_get("CLX", get = "stock.prices", from = "2024-01-01", 
               to = "2025-02-01")
CLX |>
  ggplot(aes(x = date, y = close)) +
    geom_line()  +
    geom_ma(ma_fun = SMA, n = 25, linetype = 1, size = 1.25) +
    labs(y = "Closing Price", x = "") + 
    theme_tq()
```

By playing with the "n" value - the average of the last n-day stock prices - we produced a line that closely resembles the price line. Since the SMA line crosses the price line from top to bottom, we're supposed to anticipate a drop in the stock price. 

**The Bollinger Bands** is another useful tool of technical analysis. These are "envelopes plotted at a standard deviation level above and below a simple moving average of the price" [@FinancialModelingb]. They supposed to show the volatility of a price of the stock and the size of expected change of the price in the future.

Let's demonstrate. 


```{r} 
#| echo: true
library(tidyquant)
library(ggplot2)
library(dplyr)
CLX <- tq_get("CLX", get = "stock.prices", from = "2024-01-01", 
               to = "2025-02-01")
CLX |>
  ggplot(aes(x = date, y = close, open = open,
              high = high, low = low, close = close)) +
    geom_line() +
    geom_bbands(ma_fun = SMA, sd = 2, n = 25,
                linetype = 2, size = 0.5, alpha = 0.2,
                fill        = palette_light()[[1]],
                color_bands = palette_light()[[1]],
                color_ma    = palette_light()[[2]]) +
    labs(y = "Closing Price", x = "") +
    theme_tq()
```

And finally let's look at such charts for major competitors to get the feel of the market.

```{r} 
#| echo: true
library(tidyquant)
library(ggplot2)
library(dplyr)
prices <- tq_get(c("CLX", "CL", "PG", "CHD"), get = "stock.prices", from = "2024-01-01", 
  to = "2025-02-01")
prices |>
  ggplot(aes(x = date, y = close, open = open,
              high = high, low = low, close = close)) +
    geom_line() +
    geom_bbands(ma_fun = SMA, sd = 2, n = 25,
                linetype = 2, size = 0.5, alpha = 0.2,
                fill        = palette_light()[[1]],
                color_bands = palette_light()[[1]],
                color_ma    = palette_light()[[2]]) +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    theme_tq()
```

As we can see, the volatility of the stock prices shouldn't be that great in the near future. Since technical analysis is best-suited for short-term trading, near future is all we can advise or client on based on such analysis.

### **Conclusion**

We can use "tidyquant" R language package along with other packages for producing charts to perform basic technical analysis of stock price. The analysis predicts stable performance in the short term.
